What is an Ancestral Recombination Graph?

### 2022-01-10 paper.tex
Placeholders for figures.

@@

@@

@@

>>>>

\begin{figure}
\vspace{5em}
\caption{\label{fig-pedigree-and-arg}
The (unannotated) ARG is closely related to the pedigree
graph, where each ``individual'' node is replace by two ``genome''
nodes, and edges between parents and children are only included if there is
transfer of ancestral material. We usually only include nodes in an ARG
that affect our sample, so that, for example, individuals that are ancestral
to only one sampled genome are not included.}
\end{figure}

@@

\begin{figure}
\vspace{5em}
% NB: not clear if this figure is better off on its own or should be
% merged with the pedigree one.
\caption{\label{fig-arg-annotations}
The specific path through the ARG for a given genome position (and therefore
the local genealogical tree) cannot be determined without annotations
to the graph. (A) The classical Griffiths approach annotates recombination
nodes with the corresponding breakpoint. (B) We can equivalently
annotate the \emph{edges} with the genomic intervals carrying ancestral
material. Edge annotations are somewhat more general, and have
significant computational advantages.}
\end{figure}

@@

\begin{figure}
\vspace{5em}
\caption{\label{fig-recombination-nodes}
Recombination nodes are optional in an edge-annotated ARG. (A) A simulated
ARG including all recombination nodes. (B) The same ARG with recombination
nodes removed. (C) The corresponding sequence of trees.
}
\end{figure}

@@

\begin{figure}
\vspace{5em}
\caption{\label{fig-inferred-args}
ARGs inferred by different methods from a small dataset. Notes about these
ARGs.
}
\end{figure}
